What is disputed on the web?

### 2010-01-28 papers/wicow_claimfinder/claimfinder.tex
Minor edits, mostly typographical in nature

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Dan Byler\\
       \affaddr{School of Information}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{trush@cs.berkeley.edu}
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
\and
\alignauthor Barbara Rosario\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
\alignauthor Tye Rattenbury\\
       \affaddr{Intel Principles and Practices}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{tye.l.rattenbury@intel.com}
}

@@

The web contains a vast number of documents written by a vast number of people. In many cases, these people disagree with each other, and the documents they write contain conflicting information. If a user is to extract reliable information from a the web, then it is useful for them to be able to determine when different documents disagree about a topic.

In this paper we describe a method for automatically aquiring a corpus of disputed claims from the web. We consider a claim to be {\it disputed} if some people believe both that others are making the claim, and that the claim is not true.

@@

Given a corpus of disputed claims $S$, we can identify other patterns that suggest that a claim is disputed by searching the web for contexts in which known disputed claims appear. This is an instance of the distributional hypothesis~\cite{distributional-hypothesis}, that theorises that if a pattern occurs with similar phrases filling it's slots (it is distributionally similar) then it has a similar meaning.

We believe that this corpus will be useful for many purposes. We are using it as part of our Dispute Finder~\cite{www-disputefinder} project, to automatically highlight phrases on web pages that are disputed by other sources. We are also exploring other applications of this corpus, including visualization tools that let users see what is disputed about topics they are interested in, or what has been disputed at particular times.

We are making our corpus publically available so that other researchers who believe it would be useful for them can download it. We plan to continue to update our corpus as new pages are added to the web, and to develop tool that allow people to query it in useful ways.

We believe that ours is the first attempt to automatically aquire a corpus of disputed claims.

@@

Information credibility on the web is becoming increasingly important. In the past people typically obtained information from a relatively small set of sources such as books, TV channels, and radio stations. Each of these sources had a known reputation, and had publishing barriers and quality control to make sure that all information they provided met the standards expected from that source. The web is very different. A user has access to a vast number of different sources, but a user will know the reputation of only a small subset of these. Moreover, the internet has little in the way of publishing barriers or quality control. If users are going to extract trustworthy information from the web then they need to either restrict themselves to a small set of sources that they trust, or use some kind of mechanism to determine the credibility of the information that they read.

@@

Given a document that contains information that may or may not be trustworthy, there are several ways that a reader can determine whether they should trust the information. They can check the reputation of the source; they can check whether it looks like a reliable document; or they can check whether the information in the document is consistent with information available from other sources.

To check the reputation of a source, a user can use a web site such as SourceWatch.org, which publishes manually curated information about the reputation and known biases of various sources. Trustpilot.com produce a Firefox extension that warns a user when they are looking at a web page hosted by a company that they believe is not trustworthy. Alternatively, a user can simply use a search engine such as Google to look for information about the source. These tools can be very useful; however trustworthy sources sometimes publish unreliable information. For example a source may have been misled by an unreliable source they were using themselves. Moreover, a user may have a document from a source that is not known to be reliable, and still wish to know if the information itself is trustworthy.

Researchers have identified a variety of metrics that can be used to automatically estimate the quality of a document based on looking at its content. For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{wikitrust} identifies potentially unreliable sections of an article by looking at the edit history. Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether there are videos. Fogg et al~\cite{Fogg} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing. Some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user.

In our research, we are following the third approach. We aim to inform users when information that they encounter is disputed by another source. We have built an extension to the Firefox web browser called Dispute Finder~\cite{www-disputefinder} that informs users when a web page that they are reading makes a claim that it knows to be disputed. For example, if a user is reading a page that says ``Elvis is Alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view. In the currently released version of Dispute Finder, it builds a corpus of disputed claims by allowing users to enter disputed claims manually, and scraping a small set of web sites that manually curate such claims; however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.

@@

The problem of detecting disputed claims is closely related to the well studied problem of detecting contradictions. A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true. For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''.
A claim $H$ is {\it disputed} if a document somewhere on the web suggests both that some people are claiming $H$ and that those people are wrong. For example the text ``we disagree with the assertion that the moon is made of cheese'' {\it disputes the claim} ``the moon is made of cheese''. A {\it contradiction} is logical, while a {\it dispute} is social. In order for a claim to be disputed, the authors of the documents must be aware that their is a contradiction between their beliefs.

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. de Marneffe et al~\cite{deMarneffe2008} present a taxonoby of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradiction. AuContraire~\cite{Ritter2008} uses TextRunner~\cite{textrunner} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. The RTE-3 Recognizing Textual Entailment challenge~\cite{rte-3} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

@@

\maybe{Want to apply wikify to get nouns, and then use Chi-style catagory rules to find out what catagories are disputed on the web?}

@@

We want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages. The Yahoo BOSS API does not offer the ability to request only pages updated in a given date range. We thus simulate this behaviour by instead including a literal date string in our queries. For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}. We instead search for \texttt{``it is not true that'' ``January 4 2010''}.

@@

Since we are using an existing search engine, we are limited to searching for simple text strings. This leads us to generate multiple patterns that are almost the same, other than for synonyms. E.g. ``the lie that'' vs ``the deceipt that''. We are also restricted to searching for patterns that consist entirely of either a prefix or a suffix. For example we could not search for ``say that $S$ despite'', because there is no way to require that ``despite'' and ``say that'' be in the same sentence. While we could do the search anyway, and then filter out all pages in which the parts were not in the same sentence, it would be inefficient, since many pages would not contain the pattern.

>>>>

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Dan Byler\\
       \affaddr{School of Information}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{daniel.byler@berkeley.edu}
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
\and
\alignauthor Barbara Rosario\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
\alignauthor Tye Rattenbury\\
       \affaddr{Intel Principles and Practices}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{tye.l.rattenbury@intel.com}
}

@@

The web contains a vast number of documents written by a vast number of people. In many cases, these people disagree with each other, and the documents they write contain conflicting information. For users to extract reliable information from the web, it is useful for them to be able to determine when different documents disagree about a topic.

In this paper we describe a method for automatically acquiring a corpus of disputed claims from the web. We consider a claim to be {\it disputed} if some people believe both that others are making the claim, and that the claim is not true.

@@

Given a corpus of disputed claims $S$, we can identify other patterns that suggest that a claim is disputed by searching the web for contexts in which known disputed claims appear. This is an instance of the distributional hypothesis~\cite{distributional-hypothesis}, which theorises that if a pattern occurs with similar phrases filling its slots (it is distributionally similar) then it has a similar meaning.

We believe that this corpus will be useful for many purposes. We are currently using it as part of our Dispute Finder~\cite{www-disputefinder} project to automatically highlight phrases on web pages that are disputed by other sources. We are also exploring other applications of this corpus, including visualization tools that let users see what is disputed about topics they are interested in, or what has been disputed at particular times.

We are making our corpus publicly available for other researchers to download. We plan to continue to update our corpus as new pages are added to the web, and to develop tools that allow people to query it in useful ways.

We believe that ours is the first attempt to automatically acquire a corpus of disputed claims.

@@

Information credibility on the web is becoming increasingly important. In the past people typically obtained information from a relatively small set of sources such as books, TV channels, and radio stations. Most of these sources had a known reputation, and had publishing barriers and quality control to ensure that the information they provided met the standards expected from that source. The web is very different. A user has access to a vast number of different sources, but a user will know the reputation of only a small subset of these. Moreover, the internet has little in the way of publishing barriers or quality control. If users are to extract trustworthy information from the web, they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.

@@

Given a document that contains information which may or may not be trustworthy, there are several ways that a reader can determine whether they should trust the information. They can check the reputation of the source; they can check whether it looks like a reliable document; or they can check whether the information in the document is consistent with information available from other sources.

To check the reputation of a source, a user can use a web site such as SourceWatch.org, which publishes manually curated information about the reputation and known biases of various sources. Trustpilot.com produce a Firefox extension that warns a user when they are looking at a web page hosted by a company that they believe is not trustworthy. Alternatively, a user can simply use a search engine such as Google to look for information about the source. While these tools can be very useful, trustworthy sources sometimes publish unreliable information. For example, a source may have been misled by an unreliable source they were using themselves. Moreover, a user may have a document from a source that is not known to be reliable, and still wish to know if the information itself is trustworthy.

Researchers have identified a variety of metrics that can be used to automatically estimate the quality of a document based on looking at its content. For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{wikitrust} identifies potentially unreliable sections of an article by analyzing its edit history. Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether it contains videos. Fogg et al~\cite{Fogg} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing. Some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user.

In our research, we are following the third approach. We aim to inform users when information that they encounter is disputed by another source. We have built an extension to the Firefox web browser called Dispute Finder~\cite{www-disputefinder} that informs users when a web page that they are reading makes a claim that it knows to be disputed. For example, if a user is reading a page that says ``Elvis is Alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view. In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to enter disputed claims manually, and scraping a small set of web sites that manually curate such claims; however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.

@@

The problem of detecting disputed claims is closely related to the well-studied problem of detecting contradictions. A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true. For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''.
A claim $H$ is {\it disputed} if a document somewhere on the web suggests both that some people are claiming $H$ and that those people are wrong. For example the text ``we disagree with the assertion that the moon is made of cheese'' {\it disputes the claim} ``the moon is made of cheese''. A {\it contradiction} is logical, while a {\it dispute} is social. In order for a claim to be disputed, the authors of the documents must be aware that there is a contradiction between their beliefs.

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. de Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradiction. AuContraire~\cite{Ritter2008} uses TextRunner~\cite{textrunner} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. The RTE-3 Recognizing Textual Entailment challenge~\cite{rte-3} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

@@

\maybe{Want to apply wikify to get nouns, and then use Chi-style category rules to find out what categories are disputed on the web?}

@@

We want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages. The Yahoo BOSS API does not offer the ability to request only pages updated in a given date range. We thus simulate this behaviour by instead including a literal date string in our queries. For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

@@

Since we are using an existing search engine, we are limited to searching for simple text strings. This leads us to generate multiple patterns that are almost the same, other than for synonyms. E.g. ``the lie that'' vs ``the deceit that''. We are also restricted to searching for patterns that consist entirely of either a prefix or a suffix. For example we could not search for ``say that $S$ despite'', because there is no way to require that ``despite'' and ``say that'' be in the same sentence. While we could do the search anyway, and then filter out all pages in which the parts were not in the same sentence, this would be inefficient, since many pages would not contain the pattern.
